---
title: "From MSDial on"
author: "Katherine Heal"
date: "August 11, 2020"
output: html_document
---
Organization notes:
As of 08/11/20, all mzxml and MSDial files are in corresponding Fraction/mzxml files 

Analysis notes:

```{r, message=FALSE, error=FALSE}
library(here)
```

#BMIS on the HILIC output from MSDial, save output in BMISReports Folder, remove the intermediate output
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('SourceCode/BMIS_QEHILIC.R')
ggsave("Intermediates/BMISReports/BMIS_IS_StandardsRep_HILIC.pdf", plot = BMISlist[[1]], device = "pdf", width = 10, height = 10, units = "in")
write_file(BMISlist[[2]], "Intermediates/BMISReports/BMIS_Summary_HILIC.txt")
ggsave("Intermediates/BMISReports/BMIS_IS_StandardsTest_HILIC.pdf", plot = BMISlist[[3]], device = "pdf", width = 10, height = 10, units = "in")
write_csv(BMISlist[[4]], "Intermediates/BMISReports/BMISd_Areas_long_HILIC.csv")
rm(BMISlist)
```

#BMIS on the CyanoAq output from MSDial, save output in BMISReports Folder, remove the intermediate output
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('SourceCode/BMIS_QECyanoAq.R')
ggsave("Intermediates/BMISReports/BMIS_IS_StandardsRep_Cyano.pdf", plot = BMISlist[[1]], device = "pdf", width = 10, height = 10, units = "in")
write_file(BMISlist[[2]], "Intermediates/BMISReports/BMIS_Summary_Cyano.txt")
ggsave("Intermediates/BMISReports/BMIS_IS_StandardsTest_Cyano.pdf", plot = BMISlist[[3]], device = "pdf", width = 10, height = 10, units = "in")
write_csv(BMISlist[[4]], "Intermediates/BMISReports/BMISd_Areas_long_Cyano.csv")
rm(BMISlist)
```

#BMIS on the CyanoOrg output from MSDial, save output in BMISReports Folder, remove the intermediate output
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('SourceCode/BMIS_QECyanoOrg.R')
ggsave("Intermediates/BMISReports/BMIS_IS_StandardsRep_CyanoOrg.pdf", plot = BMISlist[[1]], device = "pdf", width = 10, height = 10, units = "in")
write_file(BMISlist[[2]], "Intermediates/BMISReports/BMIS_Summary_CyanoOrg.txt")
ggsave("Intermediates/BMISReports/BMIS_IS_StandardsTest_CyanoOrg.pdf", plot = BMISlist[[3]], device = "pdf", width = 10, height = 10, units = "in")
write_csv(BMISlist[[4]], "Intermediates/BMISReports/BMISd_Areas_long_CyanoOrg.csv")
rm(BMISlist)
```

#Combine and Tidy environmental data, add in culture data, grab MS2 data
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('SourceCode/Combine_and_Tidy.R')
remove(list = ls())
```

#QC on targeted compounds from Laura C
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('SourceCode/QC_HILICPos_Targeted.R')
remove(list = ls())

source('SourceCode/QC_HILICNeg_Targeted.R')
remove(list = ls())

source('SourceCode/QC_RPAq_Targeted.R')
remove(list = ls())

source('SourceCode/QC_RPOrg_Targeted.R')
remove(list = ls())
```

#Combine and tidy targeted data
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('SourceCode/Combine_and_Tidy_Targeted.R')
remove(list = ls())

```

#Check the untargeted for the same things Laura H sfound
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('SourceCode/PreviousResultsCheck.R')

```

